---
title: "GenderGap"
author: "HyeKyung Yoon"
output: html_document
editor_options: 
  chunk_output_type: console
---

# WEEK 2 WORKSHOP

```{r setup}

library(tidyverse)
gender.gap <- read_csv("UK gender Pay Gap Data - 2017 to 2018.csv")
```

Data Dictionary

Data are from [https://data.gov.uk/dataset/54219db1-dd98-49d9-a383-a5978bb0aeb9/gender-pay-gap](https://data.gov.uk/dataset/54219db1-dd98-49d9-a383-a5978bb0aeb9/gender-pay-gap)

"The gender pay gap is the difference between the average earnings of men and women, expressed relative to men¡¯s earnings. For example, ¡®women earn 15% less than men per hour¡¯."

Details are available at [https://www.gov.uk/guidance/gender-pay-gap-reporting-overview](https://www.gov.uk/guidance/gender-pay-gap-reporting-overview) with calculation details [https://www.gov.uk/guidance/gender-pay-gap-reporting-make-your-calculations](https://www.gov.uk/guidance/gender-pay-gap-reporting-make-your-calculations)

Variable                  | Description
------------------------- | ---------------------------------------------------------
EmployeerName             | 
Adddress                  | 
CompanyNumber             | Number from Companies House
SicCodes                  | Standard industrial classification of economic activities
DiffMeanHourlyPercent     | As described at the above link: $\frac{male~mean - female~mean}{male~mean} \times 100\%$
DiffMedianHourlyPercent   | 
DiffMeanBonusPercent      | 
DiffMedianBonusPercent    | 
MaleBonusPercent          | Percentage of males receiving a bonus
FemaleBonusPercent        | 
MaleLowerQuartile         | Percentage of lower quartile that are male
FemaleLowerQuartile       | For each quartile, male and female percentages always sum to 100
MaleLowerMiddleQuartile   | 
FemaleLowerMiddleQuartile | 
MaleUpperMiddleQuartile   | 
FemaleUpperMiddleQuartile | 
MaleTopQuartile           | 
FemaleTopQuartile         | 
CompanyLinkToGPGInfo      | URL to information on individual company web sites
ResponsiblePerson         | Person responsible, often the Managing Director
EmployeerSize             | Character string with range of number of employees e.g., "500 to 999"
CurrentName               | Matches EmployerName for all but 2%
SubmittedAfterTheDeadline | Boolean; 6% of companies submitted after the deadline
DueDate                   | Either 31 March 2018 (public sector) or 5 April 2018 (businesses and charities)
DateSubmitted             | Date and time submitted; no missing data
---------------------------------------------------------------------------------------

```{r}

# Mean difference between male and female hourly pay

summarise(gender.gap, MeanDifference = mean(DiffMeanHourlyPercent))


gender.gap %>% summarise(mean(DiffMeanHourlyPercent))
```

The mean hourly pay for females is 14.3% lower than for males

```{r}

# Pay gap at Vodafone

gender.gap %>% filter(grepl("VODAFONE GROUP",EmployerName)) %>% select(ends_with("quartile"))


gender.gap %>% filter(grepl("VODAFONE", EmployerName))
gender.gap %>% filter(EmployerName=="VODAFONE GROUP SERVICES LIMITED") %>% print(width=1000)
```

The gender pay gap for Vodafone is 14.6%

```{r}

# Sketch the distribution of pay for males and females

gender.gap %>% filter(grepl("VODAFONE",EmployerName)) %>% select(starts_with("Female"))
gender.gap %>% filter(grepl("VODAFONE",EmployerName)) %>% select(starts_with("Male"))
```

```{r}

# Public sector vs. Business or Charities

public <- filter(gender.gap, DueDate=="31/03/2018 00:00:00")
business <- filter(gender.gap, DueDate=="05/04/2018 00:00:00")
summarise(public, publie.gap=mean(DiffMeanHourlyPercent))
summarise(business, business.gap=mean(DiffMeanHourlyPercent))


library(lubridate)
gender.gap <- mutate(gender.gap, DueDate=dmy_hms(DueDate), Sector=ifelse(DueDate==ymd("2018-03-31"), "Public Sector", "Business / Charity"))
gender.gap %>% summarise(n())
gender.gap %>% group_by(Sector) %>% summarise(frequency=n(), mean=mean(DiffMeanHourlyPercent))
```

The gender pay gap is larger for the public sector, at 14.9%, than for businesses or charities, where the gap is 14.2%

```{r}

# Submitted late VS. On time

sub.late <- filter(gender.gap, SubmittedAfterTheDeadline=="True")
sub.ontime <- filter(gender.gap, SubmittedAfterTheDeadline=="False")
summarise(sub.late, late=mean(DiffMeanHourlyPercent))
summarise(sub.ontime, ontime=mean(DiffMeanHourlyPercent))


gender.gap %>% group_by(SubmittedAfterTheDeadline) %>% summarise(frequency=n(), mean=mean(DiffMeanHourlyPercent))
```

Those employers submitting on time have a pay gap of 14.5%, but the 641 employers submitting late have a pay gap of 11.2%

```{r}

# Change name
gender.gap <- mutate(gender.gap, NameChange=EmployerName!=CurrentName)
gender.gap %>% group_by(NameChange) %>% summarise(frequency=n(), mean=mean(DiffMeanHourlyPercent))
```

The 178 employers that change their name have a pay gap of 15.7% compared to 14.3% for those employers who do not change their name


# WEEK 3 WORKSHOP

```{r}
library(tidyverse)
library(lubridate)
gender.gap <- read_csv("UK gender Pay Gap Data - 2017 to 2018.csv")
```

```{r}

# Historgram

ggplot(gender.gap) + geom_histogram(aes(DiffMeanHourlyPercent), binwidth= 1) + xlim(-100,100)


filter(gender.gap, abs(DiffMeanHourlyPercent)>100)
ggplot(gender.gap, aes(x=DiffMeanHourlyPercent)) + geom_histogram(binwidth=1) + xlim(-100, 100) + labs(x=expression(frac(Male~Mean-Female~Mean,Male~Mean)*'%'), y="Frequency", subtitle="NB 5 observations <-100 omitted and 1 observation>100 omitted")
```

Figure X. The distribution of gender pay gap. Pay gap is defined as the difference between mean male pay and mean female pay as a fraction of mean male pay. Bars are bins 1% wide.

```{r}

# Sector

gender.gap <- mutate(gender.gap, DueDate=dmy_hms(DueDate), Sector=ifelse(DueDate==ymd("2018-03-31"), "Public Sector", "Business / Charity"))
(gender.mean <-  gender.gap %>% group_by(Sector) %>% summarise(mean=mean(DiffMeanHourlyPercent)))
ggplot(gender.gap, aes(x=DiffMeanHourlyPercent)) + geom_histogram(binwidth = 1) + facet_grid(Sector~.) + xlim(-100,100) + geom_vline(data=gender.mean, mapping = aes(xintercept=mean)) + labs(x="mean", y="frequency", caption="some insignificant objects were deleted")


gender.gap <- mutate(gender.gap, DueDate=dmy_hms(DueDate), Sector=ifelse(DueDate==ymd("2018-03-31"), "Public Sector", "Business / Charity"))
(  gender.gap.by.sector <- gender.gap %>% group_by(Sector) %>% summarise(frequency=n(), mean=mean(DiffMeanHourlyPercent))  )
ggplot(gender.gap) + geom_histogram(aes(x=DiffMeanHourlyPercent), binwidth=1) + facet_grid(Sector~.) + xlim(-100,100) + labs(x=expression(frac(Male~Mean-Female~Mean,Male~Mean)*'%'), y="Frequency", subtitle="NB 5 observations <100 omitted and 1   observation>100 omitted") + geom_vline(data=gender.gap.by.sector, mapping=aes(xintercept=mean), col="green")
```

Figure X. The distribution of gender pay gap by industry sector. Green lines mark distribution means

```{r}

# Late vs. Ontime submission

gender.gap <- mutate(gender.gap, SubmissionTime=ifelse(SubmittedAfterTheDeadline=="True", "late", "ontime"))
(gender.sub <- gender.gap %>% group_by(SubmissionTime) %>% summarise(mean=mean(DiffMeanHourlyPercent)))
ggplot(gender.gap, aes(x=DiffMeanHourlyPercent)) + geom_histogram(binwidth = 1) + facet_grid(SubmissionTime~.,scales="free_y") + xlim(-100,100) + labs(x="mean", y="frequency")


gender.gap <- gender.gap %>% mutate(SubmittedAfterTheDeadline=factor(SubmittedAfterTheDeadline, levels=c("True", "False"), labels=c("Late Submissions", "On-Time Submissions")))
gender.gap %>% group_by(SubmittedAfterTheDeadline) %>% summarise(frequency=n(), mean=mean(DiffMeanHourlyPercent))
ggplot(gender.gap, aes(x=DiffMeanHourlyPercent)) + geom_histogram(binwidth=1) + facet_grid(SubmittedAfterTheDeadline~., scales="free_y") + xlim(-100,100) + labs(x=expression(frac(Male~Mean-Female~Mean,Male~Mean)*'%'), y="Frequency", subtitle="NB 5 observations <100 omitted and 1 observation>100 omitted")
```

Figure X. The distribution of gender pay gap by submission time. Note the change in frequency scale between panels

It is hard to see the difference in the distributions, so let's try augmenting the distributions with density plots

```{r}

# Late vs. Ontime submission Density

ggplot(gender.gap, aes(x=DiffMeanHourlyPercent, y=..density..)) + geom_histogram(binwidth = 1) + facet_grid(SubmissionTime~., scales="free_y") + xlim(-100,100) + labs(x="mean", y="frequency") + geom_density()


ggplot(gender.gap, aes(x=DiffMeanHourlyPercent, y=..density..)) + geom_histogram(binwidth=1) + facet_grid(SubmittedAfterTheDeadline~.) + xlim(-100,100) + labs(x=expression(frac(Male~Mean-Female~Mean,Male~Mean)*'%'), y="Density", subtitle="NB 5 observations <100 omitted and 1 observation>100 omitted") + geom_density()
```

Figure X. The distribution of gender pay gap by submission time. Bars show the density in 1% bins, and the black line shows the Gaussian smoothed density using Silverman's rule of thumb

See `?geom_density`, which leads you to `?bw.nrd` to find out how `geom_density()` does the smoothing


```{r}

# Draw empirical cumulative density

ggplot(gender.gap, aes(x=DiffMeanHourlyPercent, col=SubmittedAfterTheDeadline)) + stat_ecdf() + xlim(-100,100) + labs(x=expression(frac(Male~Mean-Female~Mean,Male~Mean)*'%'), y="Cumulative Density", col="Submission Timing") + scale_y_continuous(breaks=seq(0,1,0.1))
```

Figure X. The empirical cumulative density function for the gender pay gap, separated by submission timing

The distribution for late submissions is almost always to the left of the distribution for the on-time submissions, which means that the gender pay gap is a little smaller. However the CDFs cross just above the 90th percentile, which means the late submissions have the longer tail. 
